% Following CV tutorial https://latex-tutorial.com/cv-latex-guide/
\documentclass[11pt]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}

\usepackage{textcomp}
\usepackage{caption}
\usepackage{tgpagella}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{
    a4paper,
    left=20mm,
    %right=
    %bottom=
    top=15mm
}

\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{\baselineskip}{\baselineskip} % left, before, after

\pagestyle{empty}

\usepackage{enumitem}

\usepackage{sectsty}
\sectionfont {
    \raggedright
    \large
    \fontfamily{bch}\selectfont
    \sectionrule{0pt}{0pt}{-7pt}{1pt} % insert a thin rule
}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={CV - Michail Rontionov},
}

\input{macros}

\begin{document}
    \name{Michail Rontionov}

    \info{Email}{\href{mailto:mrontionov@mront.io}{mrontionov@mront.io}}
    \info{Phone}{\href{tel:+447895682664}{+44 7895 682664}}
    \info{GitHub}{\href{https://github.com/mrontio}{github.com/mrontio}}
    %\info{LinkedIn}{\href{https://www.linkedin.com/in/michail-rontionov-64810b183/}{Michail Rontionov}}
    %\info{Address}{49 Blenheim Gardens, Southampton, UK, SO17 3RN}

    \section*{Personal Profile}
    \summary{A PhD student driven by passion and people, on a path of learning and improvement. My professional interests lie in researching novel computation and machine learning, with full-stack engineering experience from Verilog, C/C++, to PyTorch.}


    \section*{Education}
    \education{iPhD in MINDS CDT}{2023}{2027}{University of Southampton}{
      \noindent Integrated PhD for the Machine Intelligence for Nano-Electronic Devices and Systems CDT.\\
      Dissertation: ``Spiking Neural Networks and Sparse Digital Architectures''. \\
      Supervisor: David Thomas. \\
      The programme offers opportunities to:
      \begin{itemize}
      \item Expand my knowledge through a interdisciplinary master's year, where I've learned about transistor manufacturing and the depths of deep learning.
      \item Improve my presentation, leadership, and management skills through training, leadership opportunities and in-house conferences.
      \end{itemize}
    }
    \education{MSci in Computer Science with a Year in Industry}{2018}{2023}{Swansea University}{
      \noindent Integrated Master's with First Class Honours. \\
      BSc Dissertation: Implementing Single-Event Upset Fault Tolerance onto a RISC-V Core, supervised by Shane Fleming.\\
      MSci Dissertation: HoP: Higher-order framework for the PYNQ FPGA Ecosystem, supervised by Cécilia Pradic.\\
      Gained experience with full-stack software engineering, digital design on FPGAs, and collaborations through courseworks and assessments.}


    \section*{Work Experience}
    \work{HPC Engineer Intern}{2020}{2021}{Intel Corporation}{
    Worked with customers to optimise applications on Intel HPC platform. Got to work with pre-production versions of Ice Lake Xeon CPUs, and Intel's first dedicated graphics product DG1. Wrote low-level applications for improved memory management, including cache-level optimisations. Maintained research lab and lead installations of tens of high-end nodes. Collaborated with senior employees to deliver complex systems for financial customers.}
    \work{Computer Science Teaching Assistant}{2019}{2023}{Swansea University}{
      Helped lecturers create ideal learning environment by checking student's lab work for correctness, and aided students in understanding of concepts and procedures.}
    \newpage
    \work{I.T. Manager}{2017}{2018}{Father's real estate company}{
    Sole I.T. employee for a team of 6 people, requiring me to manage time effectively and develop a deep understanding of the evolving computer architecture.
    }



    \section*{Volunteering}
    \volunteering{Ambassador Volunteer}{2018 --- 2020}{Technocamps}{
    Contributed time to organisation providing after-school science activities to children aged 10 to 16. Required understanding of children's intuition and develop explanations which worked for each individual, and managed the environment for a fun and engaging learning class.}
    \volunteering{Swansea University Ecological Volunteering}{2021 --- 2022}{Swansea University}{
    Cleaned up beaches and uprooted trees in Swansea's ecologically sensitive habitats to promote local flora and fauna.}
    \volunteering{General Volunteering}{2018 --- 2019}{Discovery Volunteering}{Numerous volunteering opportunities, including running events for people in need of help, preparing hygiene kits for homeless and park cleanings.}

    \section*{Skills}
    \skill{Software}{Vitis/Vivado, Linux, NixOS, Emacs, \LaTeX}
    \skill{Programming Languages}{C, C++, Python, Java, Verilog, Haskell}
    \skill{Soft Skills}{Team work, leadership, teaching, working with children, self-management, problem solving, time management}
    \skill{Physical Skills}{Computer Maintenance, Bicycle Repair, Electronics Soldering, Inventory Management}

    \section*{Interests}
    \begin{itemize}
    \item Outdoors --- Cycling, mountain biking, hiking, bouldering, running.
    \item Hobbies --- Hackathons, playing guitar, hacking emacs, homelab.
    \item Going out --- Festivals, gigs, theatre.
    \end{itemize}

\end{document}

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: t
%%% End:
